On the error performance of the $A_n$ lattices

### 2012-03-08 paper.tex
added cuberothex figure.

>>>>

\begin{figure*}[tp]
	\centering
		\includegraphics{figs/cuberothex-1.mps}
		\caption{Orthogonal projection of a cube as it is rotated about its center.  The figure of the left is the view of a cube from side on, and the boundary is a square.  When the cube is rotated the boundary becomes a hexagon.  The hexagon is regular when the cube is viewed along one of its vertices (the rightmost figure).}
		\label{fig:peplots}
\end{figure*}

This theorem asserts that the Voronoi cell of the lattice $A_n$ is the $n$-dimensional polytope that results from orthogonally projecting the $(n+1)$-dimensional into the zero sum plane.  Results of this type have been studied for some time.  A polytope that is the projection of a hypercube is called a \emph{zonotope}.
